---
title: "Fitted Models"
author: "Adam Kiehl"
date: "2022-10-11"
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rstanarm)
library(GGally)
library(ggthemes)
library(scales)
library(bayesplot)
```

```{r}
set.seed(551)
```

## Import Data

```{r}
# read data from .csv file
data_raw <- read.csv('ToyotaCorollaData.csv')

data <- data_raw %>%
  # factor categorical predictors
  mutate_at(c('Metallic', 'Automatic', 'Doors', 'Cylinders', 'Gears', 
              'Guarantee', 'BOVAG', 'Fuel_Type', 'Mfg_Month', 'Mfg_Year'),
            as.factor) %>%
  # remove singular predictor
  select(-Cylinders)

head(data)
```

Scale data and log transform `Price`.
```{r}
# log transform Price and scale predictors
data_scale <- cbind(log(data$Price),
                    (data %>% 
                       select(-Price) %>%
                       mutate_if(is.numeric, scale))) %>%
  as.data.frame()
names(data_scale) <- names(data)
```

## Diagnostic Function

```{r}
resultsDF <- data.frame(model = 1:10,
                        predictors = rep(NA, 10),
                        R2 = rep(NA, 10),
                        LOO_R2 = rep(NA, 10),
                        LOO_CV = rep(NA, 10))

# function to assess model and display examination results
diagFit <- function(fit, modelNum, results, printPlots) {
  # print model fit
  print(fit, 
        digits = 3,
        detail = FALSE)
  
  # extract number of predictors
  p <- length(fit$coefficients) - 1
  results$predictors[which(results$model == modelNum)] <- p
  
  # print model R^2 scores
  bayesR2 <- round(mean(bayes_R2(fit)), 3)
  results$R2[which(results$model == modelNum)] <- bayesR2
  print(paste('R^2: ', bayesR2))
  looR2 <- round(mean(loo_R2(fit)), 3)
  results$LOO_R2[which(results$model == modelNum)] <- looR2
  print(paste('LOO R^2: ', looR2))
  
  # print mode LOO CV score
  looFit <- loo(fit, k_threshold = 0.7)
  elpd <- round(looFit$estimates[1, 1], 2)
  # correction for log transformation of response
  if (elpd < 0) {
    looFit$pointwise[, 1] <- looFit$pointwise[, 1] + data_scale$Price
    elpd <- round(sum(looFit$pointwise[, 1]), 2)
  }
  results$LOO_CV[which(results$model == modelNum)] <- elpd
  print(paste('LOO ELPD: ', elpd))
  
  # generate QQ-Norm plot
  n <- length(fit$residuals)
  quants <- qnorm((1:n / n))
  
  plt_QQ <- ggplot(mapping = aes(x = quants, 
                                 y = sort(scale(fit$residuals)))) +
    geom_point(alpha = .5) +
    geom_abline(intercept = 0,
                slope = 1,
                col = 'red',
                size = .2) +
    labs(title = 'QQ-Norm Plot',
         x = 'Theoretical Quantiles',
         y = 'Sorted Residuals')
  
  # generate residuals vs fitted values plot
  plt_res_fit <- ggplot(mapping = aes(x = fit$fitted.values,
                                      y = fit$residuals)) +
    geom_point(alpha = .5) +
    geom_hline(yintercept = 0,
               col = 'red',
               size = .2) +
    labs(title = 'Residuals vs Fitted Values Plot',
         x = 'Fitted Values',
         y = 'Residuals')
  
  # print plots if desired
  if (printPlots) {
    print(plt_QQ)
    print(plt_res_fit)
  }
  
  return(results)
}

# Bayesian simulation size
N <- 5000

# print model diagnostic plots?
printPlots <- FALSE
```

## Model 1: Full, Unscaled, Default Priors

```{r, warning=FALSE, message=FALSE}
fit1 <- stan_glm(Price ~ .,
                 data = data,
                 refresh = 0,
                 iter = N)

resultsDF <- diagFit(fit1, 1, resultsDF, printPlots)
```

## Model 2: Full, Scaled, Default Priors

```{r, warning=FALSE, message=FALSE}
fit2 <- stan_glm(Price ~ .,
                 data = data_scale,
                 refresh = 0,
                 iter = N)

resultsDF <- diagFit(fit2, 2, resultsDF, printPlots)
```

## Model 3: Full, Scaled, Horseshoe Prior

```{r, warning=FALSE, message=FALSE}
p <- ncol(data) - 1
n <- nrow(data)

p0 <- 6

slab_scale <- sqrt(0.3 / p0) * sd(data_scale$Price)
global_scale <- (p0 / (p - p0)) / sqrt(n)

fit3 <- stan_glm(Price ~ .,
                 data = data_scale,
                 refresh = 0,
                 iter = N,
                 prior = hs(global_scale = global_scale,
                            slab_scale = slab_scale))

resultsDF <- diagFit(fit3, 3, resultsDF, printPlots)

as.data.frame(fit3) %>%
  select(-c('(Intercept)', 'sigma')) %>%
  mcmc_intervals()
```

## Model 4: Horseshoe-Selected, Scaled, Default Priors

```{r, warning=FALSE, message=FALSE}
fit4 <- stan_glm(Price ~ Age + Mfg_Month + Mfg_Year + KM + Fuel_Type + HP + 
                   Metallic + QuartTax + Weight + Guarantee + BOVAG + Period,
                 data = data_scale,
                 refresh = 0,
                 iter = N)

resultsDF <- diagFit(fit4, 4, resultsDF, printPlots)
```

## Model 5: Full, Scaled, LASSO Prior

```{r, warning=FALSE, message=FALSE}
fit5 <- stan_glm(Price ~ .,
                 data = data_scale,
                 refresh = 0,
                 iter = N,
                 prior = lasso())

resultsDF <- diagFit(fit5, 5, resultsDF, printPlots)

as.data.frame(fit5) %>%
  select(-c('(Intercept)', 'sigma')) %>%
  mcmc_intervals()
```

## Model 6: LASSO-Selected, Scaled, Default Priors

```{r, warning=FALSE, message=FALSE}
fit6 <- stan_glm(Price ~ Age + Mfg_Month + Mfg_Year + KM + Fuel_Type + HP + 
                   Metallic + QuartTax + Weight + Guarantee + BOVAG + Period,
                 data = data_scale,
                 refresh = 0,
                 iter = N)

resultsDF <- diagFit(fit6, 6, resultsDF, printPlots)
```

## Model 7: Selective, Scaled, Default Priors

```{r, warning=FALSE, message=FALSE}
fit7 <- stan_glm(Price ~ Age + KM + Fuel_Type + HP + QuartTax + Weight + 
                   Guarantee + BOVAG + Period,
                 data = data_scale,
                 refresh = 0,
                 iter = N)

resultsDF <- diagFit(fit7, 7, resultsDF, printPlots)
```

## Model 8: Selective, Unscaled, Weakly Informative Priors

```{r, warning=FALSE, message=FALSE}
priorMeans <- c(-100, -.0625, 1000, -1000, 50, 100, 10, 1000, 0, 1000)
priorVars <- c(625, .125, 62500, 62500, 100, 625, .125, 62500, 100, 62500)

fit8 <- stan_glm(Price ~ Age + KM + Fuel_Type + HP + QuartTax + Weight +
                   Guarantee + BOVAG + Period,
                 data = data,
                 refresh = 0,
                 iter = N,
                 prior = normal(priorMeans,
                                priorVars))

resultsDF <- diagFit(fit8, 8, resultsDF, printPlots)
```

## Model 9: Selective with 1 Interaction, Scaled, Default Priors

```{r, warning=FALSE, message=FALSE}
fit9 <- stan_glm(Price ~ Fuel_Type + HP + QuartTax + Weight + 
                   Guarantee + BOVAG + Period + Age*KM,
                 data = data_scale,
                 refresh = 0,
                 iter = N)

resultsDF <- diagFit(fit9, 9, resultsDF, printPlots)
```

## Model 10: Selective with 2 Interactions, Scaled, Default Priors

```{r, warning=FALSE, message=FALSE}
fit10 <- stan_glm(Price ~ Fuel_Type + HP + QuartTax + Weight + 
                    Guarantee + BOVAG + Period + Age*KM + Weight*HP,
                  data = data_scale,
                  refresh = 0,
                  iter = N)

resultsDF <- diagFit(fit10, 10, resultsDF, printPlots)
```

## Results

```{r, warning=FALSE, message=FALSE}
resultsDF
```

```{r, message=FALSE, warning=FALSE}
loo1 <- loo(fit1, k_threshold = 0.7)
loo2 <- loo(fit2, k_threshold = 0.7)
loo3 <- loo(fit3, k_threshold = 0.7)
loo4 <- loo(fit4, k_threshold = 0.7)
loo5 <- loo(fit5, k_threshold = 0.7)
loo6 <- loo(fit6, k_threshold = 0.7)
loo7 <- loo(fit7, k_threshold = 0.7)
loo8 <- loo(fit8, k_threshold = 0.7)
loo9 <- loo(fit9, k_threshold = 0.7)
loo10 <- loo(fit10, k_threshold = 0.7)

loo1$pointwise[, 1] <- loo1$pointwise[, 1] + data_scale$Price
loo8$pointwise[, 1] <- loo8$pointwise[, 1] + data_scale$Price

loo_compare(loo1, loo2, loo3, loo4, loo5, loo6, loo7, loo8, loo9, loo10)
```
